### 2018-05-17 General WLD combinatorics.tex
C(W) and R(W) dfns added in

The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams. Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$. This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.  \end{eg}

@@

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagato flat and an independent flat. \end{cor}

@@

Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or contractions of the associated matroids.

@@

\begin{figure}
 % \includegraphics{specialp}
  \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
\end{figure}

@@

\begin{figure}
%  \includegraphics{Le_diagrams}
  \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
\end{figure}

@@

  \begin{figure}
 %   \includegraphics{messy}
    \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.  The blue lines are the non-intersecting paths.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure}

@@

  \begin{figure}
    % \includegraphics{messyD}
    \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}
  \end{figure}

>>>>

The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7)\}, \{5,6,7,8,1\})$ and $(\{(5,8), (7,8)\}, \{5,6,7,8,1\})$ are the corresponding differing subdiagrams. Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$. This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.  \end{eg}

Each Wilson loop diagram, $W = (\cP, n)$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:

\ba C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
0  & \textrm{ if } q \not \in V(p)  \end{cases}
\;. \label{C(W) dfn}\ea

\begin{eg}
For example, ordering the propagators of $W_1$ above as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write 
\bas C(W_1) = \left(
\begin{array}{cccccccc}
c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
\end{array}
\right) \;.\eas

\end{eg}

These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloops}, call it $\Sigma(W)$. The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 times 1$ minors of $C(W)$ as defined below.

\begin{dfn}
For $W = (\cP, n)$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it. For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$. Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}{s-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $s = 1$, $R_e = c_{p,e} c_{p,e+1}$.
\end{dfn}

@@

Note that one may substitute values into $C(W)$ to realize the matroid assoicated to $W$ in this manner.

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagator flat and an independent flat. \end{cor}

@@

Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.

@@

\begin{figure}
 \includegraphics{specialp}
  \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
\end{figure}

@@

\begin{figure}
  \includegraphics{Le_diagrams}
  \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
\end{figure}

@@

  \begin{figure}
    \includegraphics{messy}
    \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.  The blue lines are the non-intersecting paths.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure}

@@

  \begin{figure}
     \includegraphics{messyD}
    \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}
  \end{figure}
